---
title: "vBffyR demo"
output: html_notebook
---


```{r}
library(rstan)
library(tidyverse)
library(purrr)
library(testthat)
set.seed(1)
## Load data
load("../inst/extdata/Spence_turtle_data.Rdata")
stan_dir <- "../from Mike/"
```


```{r}
list.files("../R", full.names = T) %>% map(source)
```

## Herring

### Assign species data to `df`
```{r}
nrow(her_on)
sub_rows <- 1:500
df <- her_on[sub_rows,]
```


```{r, echo = F, eval=FALSE}
# create metadata sheet shell
tibble(var_names = names(df), description = "", units = "", var_type = "") %>% write_csv("../inst/extdata/metadata.csv")
```


```{r}
df
```



```{r}
exp_df <- catch_dat_expand(df, quarter = "Quarter", age = "Age", length_class =  "LngtClass",
                 CANoAtLngt = "CANoAtLngt")


```

```{r}
h_complete_dat<-list(t = exp_df$age, l = exp_df$length_class, N = length(exp_df$age), q = exp_df$qs,mu_a=0.8576*2*pi-pi,sigma_a=0.40493)

fit_c <- stan(file = paste0(stan_dir, "vb.stan"), data = h_complete_dat, iter = 2000, chains = 1,control=list(adapt_delta=0.85,max_treedepth=10))

fit_c2 <- stan(file = paste0(stan_dir, "vb.stan"), data = h_complete_dat, iter = 2000, chains = 1,control=list(adapt_delta=0.85,max_treedepth=10))

compare(fit_c, fit_c2)

```
```{r}
summary(fit_c)
```


```{r}
plot(fit_c)
```

```{r}
traceplot(fit_c, pars = c("l_inf", "k"))
```

```{r}

h_comp_out<-extract(fit_c)
```



### Inputing data

The factor type in R is not supported as a data element for `RStan` and **must be converted to integer codes via `as.integer`**. The `Stan` modeling language distinguishes between integers and doubles (type `int` and `real` in `Stan` modeling language, respectively). The `stan` function will convert some R data (which is double-precision usually) to integers if possible.

Stan cannot handle missing values in data automatically, so no element of the data can contain NA values.
